\documentclass{article}

\title{Sequences of Ordinal Numbers. Beginnings of Ordinal Arithmetics (ORDINAL2)}
\author{Grzegorz Bancerek}
\date{July 18, 1989}
\begin{document}
\maketitle

\begin{remark}
There are about two dozen schemes in this article, and I transcribed
about half of them. I should return and continue transcribing one day.
\end{remark}

\begin{scheme}[OrdinalInd]
Let $P[-]$ be a unary predicate of Ordinals.
We have for every Ordinal $A$, $P[A]$; provided:
\begin{enumerate}
\item $P[0]$; and
\item for all Ordinals $A$, $P[A]$ implies $P[\succ(A)]$; and
\item for all nonzero limit Ordinals $A$, if every Ordinal $B\in A$
  satisfies $P[B]$, then $P[A]$.
\end{enumerate}
\end{scheme}

Let $A$, $B$, $C$ be Ordinals.
\begin{thm}
\item\label{ordinal2:1} $A\subset B$ if and only if $\succ(A)\subset\succ(B)$.
\item\label{ordinal2:2} $\union(\succ(A))=A$.
\item\label{ordinal2:3} $\succ(A)\subset\powerset(A)$.
\item\label{ordinal2:4} $0$ is a limit Ordinal.
\item\label{ordinal2:5} $\union(A)\subset A$.
\end{thm}

\begin{definition}
Let $L$ be a sequence. We define the term $\last(L)$ to be the set equal
to
\begin{defn}
\item $\last(L)=L_{\union(\dom(L))}$.
\end{defn}
\end{definition}

Let $L$ be a sequence, let $X$ and $Y$ be sets. We can now prove the
following results:
\begin{thm}
\item\label{ordinal2:6} If $\dom(L)\subset\succ(A)$, then $\last(L)=L_{A}$.
\item\label{ordinal2:7} $\On(X)\subset X$.
\item\label{ordinal2:8} $\On(A)=A$.
\item\label{ordinal2:9} If $X\subset Y$, then $\On(X)\subset\On(Y)$.
\item\label{ordinal2:10} $\Lim(X)\subset X$.
\item\label{ordinal2:11} If $X\subset Y$, then $\Lim(X)\subset\Lim(Y)$.
\item\label{ordinal2:12} $\Lim(X)\subset\On(X)$.
\item\label{ordinal2:13} Suppose every object $x\in X$ is an Ordinal.
  Then $\meet X$ is an Ordinal.
\end{thm}

Observe there exists a limit Ordinal.

\begin{definition}\index{$\inf(X)$}\index{$\sup(X)$}
Let $X$ be a set.
We define $\inf(X)$ to be the Ordinal equal to
\begin{defn}
\item $\meet\On(X)$
\end{defn}
We define $\sup(X)$ to be the Ordinal satisfying
\begin{defn}
\item $\On(X)\subset\sup(X)$, and for all Ordinals $A$ such that
  $\On(X)\subset A$ we have $\sup(X)\subset A$.
\end{defn}
\end{definition}

Let $A$, $B$, $C$, $D$ be Ordinals.
We can now prove the following results:
\begin{thm}
\item\label{ordinal2:14} If $A\in X$, then $\inf(X)\subset A$.
\item\label{ordinal2:15} If $\On(X)\neq0$ and every Ordinal $A\in X$
  contains $D\subset A$,
  then $D\subset\inf(X)$.
\item\label{ordinal2:16} If $A\in X$ and $X\subset Y$, then $\inf(Y)\subset\inf(X)$.
\item\label{ordinal2:17} If $A\in X$, then $\inf(X)\in X$.
\item\label{ordinal2:18} For any Ordinal $A$, we have $\sup(A)=A$.
\item\label{ordinal2:19} If $A\in X$, then $A\in\sup(X)$.
\item\label{ordinal2:20} Suppose every Ordinal $A\in X$ is contained in
  $A\in D$. Then $\sup(X)\subset D$.
\item\label{ordinal2:21} If $A\in\sup(X)$, then there exists an Ordinal
  $B$ such taht $B\in X$ and $A\subset B$.
\item\label{ordinal2:22} If $X\subset Y$, then $\sup(X)\subset\sup(Y)$.
\item\label{ordinal2:23} For any Ordinal $A$, we have $\sup\{A\}=A$.
\item\label{ordinal2:24} $\inf(X)\subset\sup(X)$.
\end{thm}

\begin{scheme}[TSLambda]
Let $\mathcal{A}$ be an ordinal, let $\mathcal{F}(-)$ be a set
parametrized by an ordinal.
There exists a sequence $L$ such that $\dom(L)=\mathcal{A}$ and for each
ordinal $A\in\mathcal{A}$, we have $L_{A}=\mathcal{F}(A)$.
\end{scheme}

\begin{definition}
Let $f$ be a function. We define the attribute $f$ is \define{Ordinal-yielding}
to mean
\begin{defn}
\item There exists an Ordinal $A$ such that $\rng(f)\subset A$.
\end{defn}
\end{definition}

Observe there exists an ordinal-yielding sequence.

\begin{definition}
We define the mode an \define{Ordinal-Sequence} is an Ordinal-yielding sequence.
\end{definition}

Observe a sequence of $A$ is automatically Ordinal-yielding.

Let $\varphi$, $\psi$ be Ordina-sequences. Then we can prove the
following result:
\begin{thm}
\item\label{ordinal2:25} If $A\in\dom(\varphi)$, then $\varphi_{A}$ is
  an Ordinal.
\end{thm}

Observe when we have an Ordinal-sequence $f$ and any object $a$, that
$f_{a}$ is an ordinal.

\begin{scheme}[OSLambda]
Let $\mathcal{A}$ be an Ordinal, let $\mathcal{F}(-)$ be an Ordinal
parametrized by an Ordinal.
There exists an Ordinal-sequence $\varphi$ such that $\dom(\varphi)=\mathcal{A}$
and for all Ordinals $A\in\mathcal{A}$ we have $\varphi_{A}=\mathcal{F}(A)$.
\end{scheme}

\begin{scheme}[TSUniq1]
Let $\mathcal{A}$ be an ordinal, let $\mathcal{B}$ be an object,
let $\mathcal{C}(-,-)$ be an object parametrized by an Ordinal and a set,
let $\mathcal{D}(-,-)$ be an object parametrized by an Ordinal and a Sequence,
let $\mathcal{L}_{1}$ and $\mathcal{L}_{2}$ be sequences.
We have $\mathcal{L}_{1}=\mathcal{L}_{2}$, provided:
\begin{enumerate}
\item $\dom(\mathcal{L}_{1})=\mathcal{A}$; and
\item If $0\in\mathcal{A}$, then $\mathcal{L}_{1}(0)=\mathcal{B}$; and
\item for all Ordinals $A$, if $\succ(A)\in\mathcal{A}$,
  then $\mathcal{L}_{1}(\succ(A))=\mathcal{C}(A,\mathcal{L}_{1}(A))$; and
\item for all Ordinals $A\in\mathcal{A}$, if $A\neq0$ is a limit
  ordinal,
  then $\mathcal{L}_{1}(A)=\mathcal{D}(A,\mathcal{L}_{1}|_{A})$; and
\item $\dom\mathcal{L}_{2}=\mathcal{A}$; and
\item if $0\in\mathcal{A}$, then $\mathcal{L}_{2}(0)=\mathcal{B}$; and
\item for all Ordinals $A$, if $\succ(A)\in\mathcal{A}$,
  then $\mathcal{L}_{2}(\succ(A))=\mathcal{C}(A,\mathcal{L}_{2}(A))$; and
\item for all Ordinals $A\in\mathcal{A}$, if $A\neq0$ is a limit
  ordinal,
  then $\mathcal{L}_{2}(A)=\mathcal{D}(A,\mathcal{L}_{2}|_{A})$.
\end{enumerate}
\end{scheme}

\begin{scheme}[TSExists1]
Let $\mathcal{A}$ and $\mathcal{B}$ be Ordinals, let $\mathcal{C}(-,-)$
be an object parametrized by an Ordinal and a set, let
$\mathcal{D}(-,-)$ be an object parametrized by an ordinal and a sequence.
There exists a sequence $L$ such that
\begin{enumerate}[label=(\roman*)]
\item $\dom(L)=\mathcal{A}$; and
\item if $0\in\mathcal{A}$, then $L_{0}=\mathcal{B}$; and
\item for all Ordinals $A$, if $\succ(A)\in\mathcal{A}$, then $L(\succ(A))=\mathcal{C}(A,L_{A})$;
and
\item for all Ordinals $A\in\mathcal{A}$, if $A\neq0$ is a limit
  ordinals,
  then $L(A)=\mathcal{D}(A,L|_{A})$.
\end{enumerate}
\end{scheme}

\begin{scheme}[TSResult]
Let $\mathcal{L}$ be a sequence, let $\mathcal{F}(-)$ be a set
parametrized by an Ordinal, let $\mathcal{A}$ be an Ordinal, let
$\mathcal{B}$ be a set, let $\mathcal{C}(-,-)$ be a set parametrized by
an Ordinal and a set, let $\mathcal{D}(-,-)$ be a set parametrized by an
ordinal and a sequence.
We have for all Ordinals $A\in\dom(\mathcal{L})$, $\mathcal{L}(A)=\mathcal{F}(A)$;
provided:
\begin{enumerate}
\item for all Ordinals $A$ and objects $x$, we have $x=\mathcal{F}(A)$
  if and only if there exists a sequence $L$ such that $x=\last(L)$ and
  $\dom(L)=\succ(A)$ and $L_{0}=\mathcal{B}$ and (for all Ordinals $C$
  such that $\succ(C)\in\succ(A)$ we have $L(C)=\mathcal{C}(C,L(C))$)
  and (every Ordinal $C\in\succ(A)$ which is a nonzero limit ordinal
  satisfies $L_{C}=\mathcal{D}(C,L|_{C})$); and
\item if $0\in\mathcal{A}$, then $\mathcal{L}(0)=\mathcal{B}$; and
\item for all Ordinals $A$, if $\succ(A)\in\mathcal{A}$,
  then $\mathcal{L}(\succ(A))=\mathcal{C}(A,\mathcal{L}({A}))$; and
\item for all Ordinals $A\in\mathcal{A}$, if $A\neq0$ is a limit
  ordinal, then $\mathcal{L}(A)=\mathcal{D}(A,\mathcal{L}|_{A})$.
\end{enumerate}
\end{scheme}

\begin{scheme}[TSDef]
Let $\mathcal{A}$ be an Ordinal, $\mathcal{B}$ be a set,
$\mathcal{C}($Ordinal,set$)$ be a set parametrized by an Ordinal and set,
let $\mathcal{D}($Ordinal,Sequence$)$ be a set parametrized by an
Ordinal and a set.
There exists an object $x$ and a sequence $L$ such that
\begin{enumerate}[label=(\roman*)]
\item $x=\last(L)$; and
\item $\dom(L)=\succ(\mathcal{A})$; and
\item $L(0)=\mathcal{B}$; and
\item for all Ordinals $C$, if $\succ(C)\in\succ(\mathcal{A})$,
  then $L(\succ(C))=\mathcal{C}(C,L(C))$; and
\item for all nonzero limit Ordinals $C$, if $C\in\mathcal{A}$,
  then $L(C)=\mathcal{D}(C,L|_{C})$; and
\item for all sets $x_{1}$ and $x_{2}$ such that there exists sequences
  $L_{1}$ and $L_{2}$ which satisfy $x_{1}=\last(L_{1})$ and
  $x_{2}=\last(L_{2})$ and both $L_{1}$ and $L_{2}$ satisfy the previous
  four conditions that $L$ satisfies, then $x_{1}=x_{2}$.
\end{enumerate}
\end{scheme}

\begin{scheme}[TSResult0]
Let $\mathcal{F}(-)$ be a set parametrized by an Ordinal, let
$\mathcal{B}$ be a set, let $\mathcal{C}(-,-)$ be a set parametrized by
an Ordinal and a set, let $\mathcal{D}(-,-)$ be a set parametrized by an
Ordinal and a sequence.

We have $\mathcal{F}(0)=\mathcal{B}$; provided
\begin{enumerate}
\item for all Ordinals $A$ and sets $x$, we have $x=\mathcal{F}(A)$ if
  and only if there exists a sequence $L$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $x=\last(L)$; and
  \item $\dom(L)=\succ(A)$; and 
  \item $L(0)=\mathcal{B}$; and
  \item for all Ordinals $C$, if $\succ(C)\in\succ(A)$, then
    $L(\succ(C))=\mathcal{C}(C,L(C))$; and
  \item for all nonzero limit Ordinals $C$, if $C\in\succ(A)$, then $L(C)=\mathcal{D}(C,L|_{C})$.
  \end{enumerate}
\end{enumerate}
\end{scheme}

\begin{scheme}[TSResultS]
Let $\mathcal{B}$ be a set, $\mathcal{C}(-,-)$ be a set parametrized by
an Ordinal and a set, let $\mathcal{D}(-,-)$ be a set parametrized by an
Ordinal and a Sequence, let $\mathcal{F}(-)$ be a set parametrized by an
Ordinal.

We have for all Ordinals $A$, $\mathcal{F}(\succ(A))=\mathcal{C}(A,\mathcal{F}(A))$;
provided:
\begin{enumerate}
\item for all Ordinals $A$ and sets $x$, we have $x=\mathcal{F}(A)$ if
  and only if there exists a sequence $L$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $x=\last(L)$; and
  \item $\dom(L)=\succ(A)$; and 
  \item $L(0)=\mathcal{B}$; and
  \item for all Ordinals $C$, if $\succ(C)\in\succ(A)$, then
    $L(\succ(C))=\mathcal{C}(C,L(C))$; and
  \item for all nonzero limit Ordinals $C$, if $C\in\succ(A)$, then $L(C)=\mathcal{D}(C,L|_{C})$.
  \end{enumerate}
\end{enumerate}
\end{scheme}

\begin{scheme}[TSResultL]
Let $\mathcal{L}$ be a sequence, let $\mathcal{A}$ be an Ordinal,
let $\mathcal{F}(-)$ be a set parametrized by an Ordinal, let $\mathcal{B}$
be a set, let $\mathcal{C}(-,-)$ be a set parametrized by an Ordinal and
a set, let $\mathcal{D}(-,-)$ be a set parametrized by an Ordinal and a
seqence.

We have $\mathcal{F}(\mathcal{A})=\mathcal{D}(\mathcal{A},\mathcal{L})$;
provided:
\begin{enumerate}
\item for all Ordinals $A$ and sets $x$, we have $x=\mathcal{F}(A)$ if
  and only if there exists a sequence $L$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $x=\last(L)$; and
  \item $\dom(L)=\succ(A)$; and 
  \item $L(0)=\mathcal{B}$; and
  \item for all Ordinals $C$, if $\succ(C)\in\succ(A)$, then
    $L(\succ(C))=\mathcal{C}(C,L(C))$; and
  \item for all nonzero limit Ordinals $C$, if $C\in\succ(A)$, then $L(C)=\mathcal{D}(C,L|_{C})$.
  \end{enumerate}
\item $\mathcal{A}\neq0$; and
\item $\mathcal{A}$ is a limit ordinal; and
\item $\dom(\mathcal{L})=\mathcal{A}$; and
\item for all Ordinals $A$, if $A\in\mathcal{A}$, then $\mathcal{L}(A)=\mathcal{F}(A)$.
\end{enumerate}
\end{scheme}

\begin{scheme}[OSExist]
Let $\mathcal{A}$ and $\mathcal{B}$ be Ordinals, let $\mathcal{C}(-,-)$
be an Ordinal parametrized by Ordinals, $\mathcal{D}(-,-)$ be an Ordinal
parametrized by an Ordinal and a Sequence.

There exists a Ordinal-sequence $\varphi$ such that
\begin{enumerate}[label=(\roman*)]
\item $\dom(\varphi)=\mathcal{A}$; and
\item If $0\in\mathcal{A}$, then $\varphi(0)=\mathcal{B}$;
\item For all Ordinals $A$, if $\succ(A)\in\mathcal{A}$, then $\varphi(\succ(A))=\mathcal{C}(A,\varphi(A))$;
and
\item for all nonzero limit Ordinals $A\in\mathcal{A}$, we have $\varphi(A)=\mathcal{D}(A,\varphi|_{A})$.
\end{enumerate}
\end{scheme}

\begin{scheme}[OSResult]
Let $\mathcal{P}$ be an Ordinal-Sequence, let $\mathcal{F}(-)$ be an
Ordinal parametrized by Ordinals, let $\mathcal{A}$ and $\mathcal{B}$ be
Ordinals, let $\mathcal{C}(-,-)$ be an Ordinal parametrized by two
Ordinals, and let $\mathcal{D}(-,-)$ be an Ordinal parametrized by an
Ordinal and a Sequence.

For every Ordinal $A$, if $A\in\dom(\mathcal{P})$, then $\mathcal{P}(A)=\mathcal{F}(A)$;
provided:
\begin{enumerate}
\item For all ordinals $A$ and $B$, we have $B=\mathcal{F}(A)$ if and
  only if there exists an Ordinal-sequence $\varphi$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $B=\last(\varphi)$; and
  \item $\dom(\varphi)=\succ(A)$; and
  \item $\varphi(0)=\mathcal{B}$; and
  \item every Ordinal $C$, if $\succ(C)\in\succ(A)$, then
    $\varphi(\succ(C))=\mathcal{C}(C,\varphi(C))$; and
  \item every nonzero limit Ordinal $C$ satisfies $\varphi(C)=\mathcal{D}(C,\varphi|_{C})$;
  \end{enumerate}
\item $\dom(\mathcal{P})=\mathcal{A}$; and
\item If $0\in\mathcal{A}$, then $\mathcal{P}(0)=\mathcal{B}$; and
\item For all Ordinals $A$, if $\succ(A)\in\mathcal{A}$, then
  $\mathcal{P}(\succ(A))=\mathcal{C}(A,\mathcal{P}(A))$; and
\item Every nonzero limit Ordinal $A\in\mathcal{A}$ satisfies $\mathcal{P}(A)=\mathcal{D}(A,\mathcal{P}|_{A})$.
\end{enumerate}
\end{scheme}

\begin{scheme}[OSDef]

\end{scheme}

\begin{definition}\index{Sequence!Supremum}\index{$\sup(L)$}\index{Supremum!Sequence}\index{Sequence!Infinimum}\index{$\inf(L)$}\index{Infinimum!Sequence}
Let $L$ be a Sequence.
We define $\sup(L)$ to be the Ordinal equal to
\begin{defn}
\item $\sup(L):=\sup(\rng(L))$
\end{defn}
We define $\inf(L)$ to be the Ordinal equal to
\begin{defn}
\item $\inf(L):=\inf(\rng(L))$
\end{defn}
\end{definition}

We can prove the following proposition:
\begin{thm}
\item\label{ordinal2:26} 
\end{thm}

\begin{definition}\index{$\liminf(L)$}\index{$\limsup(L)$}
Let $L$ be a sequence. We define $\limsup(L)$ to be the Ordinal
satisfying
\begin{defn}
\item There exists an Ordinal-sequence $\varphi$
  such that $\limsup(L)=\inf(\varphi)$
  and $\dom(\varphi)=\dom(L)$ and
  every Ordinal $A\in\dom(L)$ satisfies
  $\varphi(A)=\sup(\rng(L|_{\dom(L)\setminus A}))$.
\end{defn}
We define $\liminf(L)$ to be the Ordinal satisfying
\begin{defn}
\item There exists an Ordinal-sequence $\varphi$ such that
  $\liminf(L)=\sup(\varphi)$ and $\dom(\varphi)=\dom(L)$ and every
  Ordinal $A\in\dom(L)$ satisfies
  $\varphi(A)=\inf(\rng(L|_{\dom(L)\setminus A}))$.
\end{defn}
\end{definition}

\begin{definition}
Let $A$ be an Ordinal, let $\varphi$ be an Ordinal-sequence.
We define the predicate \define{$A$ is the limit of $\varphi$}
(Mizar: ``\verb#A is_limes_of fi#'')
is defined by
\begin{defn}
\item Per cases by $A$:
  \begin{enumerate}[label=(\roman*)]
  \item (When $A=0$): There exists an Ordinal $B\in\dom(\varphi)$ such that for every
    Ordinal $C$, if $B\subset C$ and $C\in\dom(\varphi)$, then $\varphi(C)=0$;
  \item (Otherwise) For all Ordinals $B$ and $C$, if $B\in A$ and $A\in C$, 
    then there exists an Ordinal $D\in\dom(\varphi)$ such that every
    Ordinal $E\in\dom(\varphi)$ satisfies if $D\subset E$ then
    $B\in\varphi(E)$ and $\varphi(E)\in C$.
  \end{enumerate}
\end{defn}
\end{definition}

\begin{definition}
Let $\varphi$ be an Ordinal-sequence. Assume there exists an Ordinal
which is the limit of $\varphi$.
Then we define the term \define{the limit of $\varphi$} (Mizar:
``\verb#lim fi#'') is the Ordinal satisfying:
\begin{defn}
\item it is the limit of $\varphi$.
\end{defn}
\end{definition}

\begin{definition}\index{$\lim_{A}\varphi$}
Let $A$ be an Ordinal, let $\varphi$ be an Ordinal-sequence.
We define the term $\lim_{A}\varphi$ (Mizar: ``\verb#lim(A,fi)#'')
to be the Ordinal equal to
\begin{defn}
\item $\lim_{A}\varphi=\lim\varphi|_{A}$.
\end{defn}
\end{definition}

\begin{definition}
Let $L$ be an Ordinal-sequence.
We define the attribute $L$ is \define{increasing} to mean
\begin{defn}
\item For all Ordinals $A\in B$ and $B\in\dom(L)$, we have $L(A)\in L(B)$.
\end{defn}
We define the attribute $L$ is \define{continuous} to mean
\begin{defn}
\item For all Ordinals $A\in\dom(L)$ and $B=L(A)$, if $A\neq 0$ is a
  limit ordinal, then $B$ is the limit of $L|_{A}$.
\end{defn}
\end{definition}

\begin{definition}\index{Ordinal!Addition}
Let $A$ and $B$ be Ordinals.
We define the term $A+B$ (Mizar: ``\verb#A +^ B#'') to be the Ordinal
satisfying
\begin{defn}
\item There exists an Ordinal-sequence $\varphi$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $A+B=\last(\varphi)$, and
  \item $\dom(\varphi)=\succ(B)$, and
  \item $\varphi(0)=A$, and
  \item for all Ordinals $C$, if $\succ(C)\in\succ(B)$, then $\varphi(\succ(C))=\succ(\varphi(C))$,
    and
  \item for all nonzero limit Ordinals $C$, if $C\in\succ(B)$, then $\varphi(C)=\sup(\varphi|_{C})$.
  \end{enumerate}
\end{defn}
\end{definition}

\begin{remark}
Intuitively, this means that $\varphi_{0}=A$ and $\varphi_{n+1}=1+\varphi_{n}$
and $A+B=\varphi_{B}$. Observe this gives us the identity $A+0=A$ automatically.
\end{remark}

\begin{definition}\index{Ordinal!Multiplication}
Let $A$ and $B$ be Ordinals.
We define the term $A\cdot B$ (Mizar: ``\verb#A *^ B#'')
to be the Ordinal satisfying
\begin{defn}
\item There exists an Ordinal-sequence $\varphi$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $A\cdot B=\last(\varphi)$; and
  \item $\dom(\varphi)=\succ(A)$; and
  \item $\varphi(0)=0$; and
  \item for all Ordinals $C$, if $\succ(C)\in\succ(B)$,
    then $\varphi(\succ(C))=\varphi(C)+B$;
    and
  \item for all nonzero limit Ordinals $C$, if $C\in\succ(B)$, then $\varphi(C)=\union(\sup(\varphi|_{C}))$.
  \end{enumerate}
\end{defn}
\end{definition}

\begin{remark}
Intuitively, this means for $A\cdot B$ that $\varphi_{0}=0$ and
$\varphi_{n+1}=\varphi_{n}+B$, so $A\cdot B=\varphi_{A}$. This gives us
$0\cdot B=0$ automatically.
\end{remark}

\begin{definition}
Let $A$ and $B$ be Ordinals.
We define the term $A^{B}$ (Mizar: ``\verb#exp(A,B)#'') to be the
Ordinal satisfying
\begin{defn}
\item There exists an Ordinal-sequence $\varphi$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $A^{B}=\last(\varphi)$; and
  \item $\dom(\varphi)=\succ(B)$; and
  \item $\varphi(0)=1$; and
  \item for all Ordinals $C$, if $\succ(C)\in\succ(B)$,
    then $\varphi(\succ(C))=A\cdot\varphi(C)$;
    and
  \item for all nonzero limit Ordinals $C$, if $C\in\succ(B)$, then $\varphi(C)=\lim(\varphi|_{C})$.
  \end{enumerate}
\end{defn}
\end{definition}

\begin{remark}
Observe, for $A^{B}$, this intuitively is encoded by $\varphi_{0}=1$ and
$\varphi_{n+1}=A\cdot\varphi_{n}$. 
\end{remark}

We can now prove the following results:
\begin{thm}
\item\label{ordinal2:27} $A+0=A$.
\item\label{ordinal2:28} $A+\succ(B)=\succ(A+B)$.
\item\label{ordinal2:29} Let $B\neq0$ is a limit ordinal. If every
  Ordinal-sequence $\varphi$ such that $\dom(\varphi)=B$ and every
  Ordinal $C\in B$ satisfies $\varphi(C)=A+C$,
  then $A+B=\sup(\varphi)$.
\item\label{ordinal2:30} $0+A=A$.
\item\label{ordinal2:31} $A+1=\succ(A)$.
\item\label{ordinal2:32} If $A\in B$, then $C+A\in C+B$.
\item\label{ordinal2:33} If $A\subset B$, then $C+A\subset C+B$.
\item\label{ordinal2:34} If $A\subset B$, then $A+C\subset B+C$.
\item\label{ordinal2:35} $0\cdot A=0$.
\item\label{ordinal2:36} $(\succ(B))\cdot A=B\cdot A+A$.
\item\label{ordinal2:37} Let $B$ be a nonzero limit Ordinal.
  Let $\varphi$ be an Ordinal Sequence. If $\dom(\varphi)=B$ and every
  Ordinal $C\in B$ satisfies $\varphi(C)=C\cdot A$, then $B\cdot A=\union(\sup(\varphi))$.
\item\label{ordinal2:38} $A\cdot 0=0$.
\item\label{ordinal2:39} $1\cdot A=A$ and $A\cdot 1=A$.
\item\label{ordinal2:40} If $C\neq0$ and $A\in B$, then $A\cdot C\in B\cdot C$.
\item\label{ordinal2:41} If $A\subset B$, then $A\cdot C\subset B\cdot C$.
\item\label{ordinal2:42} If $A\subset B$, then $C\cdot A\subset C\cdot B$.
\item\label{ordinal2:43} $A^{0}=1$.
\item\label{ordinal2:44} $A^{\succ(B)}=A\cdot A^{B}$.
\item\label{ordinal2:45} Let $B$ be a nonzero limit Ordinal, let
  $\varphi$ be an Ordinal Sequence. If $\dom(\varphi)=B$ and every
  Ordinal $C\in B$ satisfies $\varphi(C)=A^{C}$, then $A^{B}=\lim\varphi$.
\item\label{ordinal2:46} $A^{1}=A$ and $1^{A}=1$.
\item\label{ordinal2:47} For any Ordinal $A$ there exists Ordinals $B$
  and $C$ such that $B$ is a limit Ordinal and $C$ is natural and $A=B+C$.
\end{thm}

\begin{definition}
Let $A$ and $B$ be Ordinals.
We define the predicate $A$ is \define{Cofinal} with $B$ to mean
\begin{defn}
\item There exists an Ordinal-Sequence $\xi$ such that
  \begin{enumerate}[label=(\roman*)]
  \item $\dom(\xi)=B$, and
  \item $\rng(\xi)\subset A$, and
  \item $\xi$ is increasing, and
  \item $A=\sup(\xi)$.
  \end{enumerate}
\end{defn}
Observe every Ordinal is cofinal with itself (i.e., Cofinality is a
reflexive predicate).
\end{definition}

Let $X$, $Y$ be sets. Let $\psi$ be an Ordinal-sequence.
We can now prove the following three propositions:
\begin{thm}
\item\label{ordinal2:48} If $X\in\rng(\psi)$, then $X$ is an Ordinal.
\item\label{ordinal2:49} $\rng(\psi)\subset\sup(\psi)$.
\item\label{ordinal2:50} If $A$ is cofinal with 0, then $A=0$.
\end{thm}

\end{document}