\documentclass{article}
\title{Introduction to Arithmetic of Real Numbers (XREAL-0)}
\author{Library Committee}
\date{February 11, 2003}
\begin{document}
\maketitle
\begin{definition}
Let $r$ be an object.
We define the attribute, saying $r$ is \define{real} to mean
\begin{defn}
\item $r\in\RR$.
\end{defn}
\end{definition}
Observe all elements of $\RR$ automatically are real.
We also observe that $-\infty$ is nonreal, and $+\infty$ is nonreal.

We observe every natural object is real, and every real object is
complex.

Observe there exists a real object, there exists a real number, and
every real object is also ext-real.

\begin{definition}
We define the mode, a \define{Real} is a real Number.
\end{definition}

Let $x$ be any Real. Observe $-x$ is real, $x^{-1}$ is real. Further,
let $y$ be any Real. Observe $x+y$ is real, $x\cdot y$ is real, $x-y$ is
real, and $x/y$ is real.

Observe there exists a positive Real, a negative Real, and a zero Real.

Let $r$ and $s$ be nonnegative Reals. Then $r+s$ is nonnegative.

Let $r$ and $s$ be nonpositive Reals. Then $r+s$ is nonpositive.

Let $r$ be a positive Real, let $s$ be a nonnegative Real. Then $r+s$
and $s+r$ are both positive.

Let $r$ be a negative Real, let $s$ be a nonpositive Real. Then $r+s$
and $s+r$ are both negative.

Let $r$ be a nonpositive Real. Then $-r$ is nonnegative.

Let $r$ be a nonnegative Real. Then $-r$ is nonpositive.

Let $r$ be a nonnegative Real, let $s$ be a nonpositive Real.
Then $r-s$ is nonnegative, and $s-r$ is nonpositive.

Let $r$ be a positive Real, let $s$ be a nonpositive Real.
Then $r-s$ is positive, and $s-r$ is negative.

Let $r$ be a negative Real, let $s$ be a nonnegative Real.
Then $r-s$ is negative, and $s-r$ is positive.

Let $r$ be a nonpositive Real, let $s$ be a nonnegative Real.
Then $r\cdot s$ and $s\cdot r$ are both nonpositive.

Let $r$ and $s$ be nonpositive Reals. Then $r\cdot s$ is nonnegative.

Let $r$ and $s$ be nonnegative Reals. Then $r\cdot s$ is nonnegative.

Let $r$ be a positive Real. Then $r^{-1}$ is positive.

Let $r$ be a nonpositive Real. Then $r^{-1}$ is nonpositive.

Let $r$ be a negative Real. Then $r^{-1}$ is negative.

Let $r$ be a nonnegative Real. Then $r^{-1}$ is nonnegative.

Let $r$ be a nonnegative Real, let $s$ be a nonpositive Real.
Then $r/s$ and $s/r$ are both nonpositive.

Let $r$ and $s$ be nonnegative Reals.
Then $r/s$ is nonnegative.

Let $r$ and $s$ be nonpositive Reals.
Then $r/s$ is nonnegative.

Let $r$ and $s$ be Reals.
Then $\min(r,s)$ and $\max(r,s)$ are both real.

\begin{definition}
Let $r$ and $s$ be Reals.
We define the term $r-s$ (Mizar: ``\verb#r -' s#'') to be the set equal
to
\begin{defn}
\item $r-s$ if $r-s\geq0$, otherwise $0$.
\end{defn}
\end{definition}

Let $r$, $s$ be Reals.
Observe $r-s$ is nonnegative.

We can check the sethood property holds for Reals.

Let $x$ be a Real.
We can reduce $\In{x}{\RR}$ to $x$.

\end{document}